---
title: "Geoconnex Demo"
author: "dblodgett@usgs.gov"
date: "11/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(dplyr, quietly = TRUE)
```

What's available from info.geoconnex.us?
```{r}
collection_url <- "https://info.geoconnex.us/collections"
collections <- jsonlite::fromJSON(collection_url)

knitr::kable(select(collections$collections, title, description))
```

Let's use New Mexico as our area of interest.

```{r}
nm_url <- "https://info.geoconnex.us/collections/states/items?STUSPS=NM"
nm <- sf::read_sf(nm_url)
mapview::mapview(list(`New Mexico` = nm))
```

The search above gave us one state that we can retrieve by it's ID. Below, we grab its JSON-LD format. Below, we print two text of what can be interpreted 

```{r}
accept_jsonld <- httr::add_headers("Accept" = "application/ld+json")

nm_ld <- rawToChar(httr::GET(nm$id, config = accept_jsonld)$content)

prettify(nm_ld)

nm_ld <- jsonld::jsonld_flatten(nm_ld)

nm_ld

nm_ld <- fromJSON(nm_ld)
```

This gives us some basic information. The `@id` here is especially useful. Note that the `@id` (the subject of all the triples in the document) is the same as the `id` of the State GeoJSON we mapped above and used to retrieve this JSON-LD document. 

Notice that we can get a name using a linked data property `https://schema.org/name` here. This is an example of structured data that would allow automated creation of information products that is an aim of geoconnex.us.

```{r}

nm_feature <- sf::read_sf(nm_ld$`@id`)

nm_feature_name <- nm_ld$`https://schema.org/name`[[1]]$`@value`

# Could make html links clickable in mapview

nm_map_layer <- setNames(list(nm_feature), nm_feature_name)

mapview::mapview(nm_map_layer)

```

Now let's pivot to look at some data that's available for NM. For this example, let's first find all the HUC08s in NM. For this example, we'll use a spatial intersection, but as geoconnex grows, these kinds of queries will be possible directly in the linked data.

```{r}

hu08_url <- paste0("https://info.geoconnex.us/collections/hu08/items?bbox=",
                   paste(sf::st_bbox(nm_feature), collapse = ","))

hu08 <- sf::read_sf(hu08_url)

mapview::mapview(list("HUC8" = hu08))

```
Now let's zoom in and look at the Pecos Headwaters HU08.

```{r}

hu08 <- filter(hu08, grepl("Pecos Headwaters", NAME))

mapview::mapview(setNames(list(hu08), hu08$NAME))

```

First, let's look at what community reference stream gages are in this HU08

```{r}

stream_gages_url <- paste0("https://info.geoconnex.us/collections/gages/items?bbox=",
                           paste(sf::st_bbox(hu08), collapse = ","))

stream_gages <- sf::st_intersection(sf::read_sf(stream_gages_url),
                                    hu08)

mapview::mapview(stream_gages)

```

Browsing around these sites a bit, let's use the [PECOS RIVER NEAR PUERTO DE LUNA, NM.](https://waterdata.usgs.gov/monitoring-location/08383500/) Since the reference gages include network locations on the NHDPlusV2, we can use them with the [Hydro Network Linked Data Index.](https://waterdata.usgs.gov/blog/nldi-intro/). 

We can use the R package, `nhdplusTools` to interact with the NLDI. Below, we get the basin boundary, mainstem, and all sites in the Western States Water Councile Water Data Exchange upstream of this stream gage.

```{r}
site <- filter(stream_gages, name == "PECOS RIVER NEAR PUERTO DE LUNA, NM")

nldi_feature <- list(featureSource = "nwissite", 
                     featureID = paste0("USGS-", site$provider_id))

basin <- nhdplusTools::get_nldi_basin(nldi_feature)

mainstem <- nhdplusTools::navigate_nldi(nldi_feature, "UM", "flowlines", distance_km = 500)

wade <- nhdplusTools::navigate_nldi(nldi_feature, "UM", "wade", distance_km = 500)

mapview::mapview(wade) + mapview::mapview(sf::st_geometry(mainstem)) + mapview::mapview(hu08)
```

```{r}
nm_wells_base_url <- "https://st.newmexicowaterdata.org/FROST-Server/v1.1/Locations?$resultFormat=GeoJSON&$skip="

nr <- 1
i <- 1
skip <- 0
out <- rep(list(list()), 100)

while(nr > 0) {
  out[i] <- list(sf::read_sf(paste0(nm_wells_base_url, skip)))
  
  out[i][[1]] <- out[i][[1]][, !colSums(is.na(out[i][[1]])) == nrow(out[i][[1]])]
  
  nr <- nrow(out[i][[1]])
  skip <- skip + 200
  i <- i + 1
}

nm_wells <- bind_rows(out[1:(i-1)])

nm_wells <- sf::st_intersection(nm_wells, hu08)

mapview::mapview(hu08) + mapview::mapview(nm_wells)
```
